Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-11-12 ms.tex
fitting the 1/f noise as an example
showing asic voltages w/ time series

@@

>>>>

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{pixeltime_series_amp_0_full_fft_cleaned_True.pdf}
\caption{The discreet Fourier transform of the entire time series from one amplifier shows 1/f noise at low frequencies that levels off at high frequencies.
}\label{fig:pixelTSeriesFFT}
\end{figure*}

@@

\subsection{Asic Voltages}
\begin{figure*}
\gridline{
\fig{individual_azlab07_baseline2_487_and_490_binned.pdf}{0.89\textwidth}{Asic Voltages and Detector fluxes on 487 and 489}\\
}
\caption{Asic voltages do not show obvious strong correlations with flux. There's a slight correlation with VRST\_V.
}\label{fig:asicVoltageAndFlux}
\end{figure*}
